---
title: "W_UP_01"
author: "Jordan Rose"
date: "fall 2020"
output: html_document
---



The report structure should include five sections.  see below



```{r include=FALSE,echo=FALSE}
require(tigerstats)
require(tidyverse)
mydata <- read.csv(file="pushups.csv")
```

# Introduction

<!--In this section you explain what you are trying to show. Where did the data come from? What is the research or other question you are trying to answer?!-->

Create an Rstudio project in your shared space on rstudio.cloud.  Using the dataset called pushups from the tigerstats package in R; answer the question posed by this null and alternate hypothesis in an html markdown document.

$H_0$: There is no difference between the average number of pushups of line vs skill players

$H_A$: The average number of pushups done by line players is statistically different than that of skill players.

# Methods

<!--Decide on your methods: use "variable analysis" or other appropriate descriptors. Make sure to choose at least one graphical method and at least one numerical method.!-->

# Results

<!--Divide this section into two sub-sections: One for your descriptive results and one for your inferential results.!-->

## Descriptive Results

### Graphical Descriptive Results

<!--Graphical results here. Make sure to show your code. Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too. Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question!-->

### Plot boxplots

```{r}
boxplot(pushups~position,data=mydata)
```

The skilled players exhibit a much higher average number of pushups in comparison to the line players. We see this here in the box and whisker plot as it shows the median for the line players at about 18 pushups. The median for the the skilled players stands around the number 50, which is much more significant than that of the line players. 

### Numerical Descriptive Results

<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->

# Numerical results

```{r}
favstats(pushups~position,data=mydata)
```

In this illustration of these numerical results we can see that the Line postions start at a minimum of 6 pushups while the highest they can do is at 34. In terms of the skilled players we see that their minimum amount of pushups is about 18 while there is median amount of pushups supersedes the line players median amount by quadruple the amount.  

## Inferential Results

<!--State hypothesis clearly. Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc. Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->

# Inferential  
  
```{r}
t.test(pushups~position,data=mydata)
```

The average or mean is illustrated here with the LINE group at 17.12500 while the mean of the SKILL is at 49.7272.
The p value is equal to 9.421

# Discussion and Conclusion

<!--Discussion and conclusion here. If you found a relationship be sure to consider whether the relationship occurs because one of the variavbles causes the other, or whether they perhasps are related for some other reason. Watch the chapter 6 videos from the GeorgeTown videos collection.!-->

There is a significant difference of the LINE positions between the SKILL positions in terms of which postion can do more pushups. The average number of LINE positions is at 17.12500 which is far less significant than those in the SKILL positions which is at 49.7272. Therefore we can say that the SKILL positions are able to do much more pushups compared to the LINE positions on average. 

